%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Chinmay Dali} \\ \vspace{1pt}
    {\faIcon{phone} \href{tel:+15512152071}{\small 551-215-2071}} $|$ 
    {\faIcon{envelope} \href{mailto:cdali@stevens.edu}{\underline{\small cdali@stevens.edu}}} $|$ 
    {\faIcon{linkedin} \href{https://linkedin.com/in/chinmay-395/}{\small chinmay-395}} $|$
    {\faIcon{github} \href{https://github.com/Chinmay-395}{\small Chinmay-395}} $|$
    {\faIcon{globe} \href{https://chinmay-dali-395.herokuapp.com}{\underline{\small portfolio}}}
    
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Stevens Institute of Technology}{Hoboken, NJ}
      {Masters of Science in Computer Science}{Aug. 2022 -- May 2024}
    \resumeSubheading
      {University Of Mumbai}{Mumbai, India}
      {Bachelor of Engineering in Computer Engineering}{Aug. 2017 -- May 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Associate Software Engineer}{Aug. 2021 -- Feb. 2022}
      {ONETURE TECHNOLOGIES} {Mumbai, India}
      \resumeItemListStart
            \resumeItem{Achieved \textbf{20\%} improvement in performance in \textbf{ASP.NET} application by server side caching \newline and build \textbf{REST APIs} with \textbf{99\%+} up-time. }
            \resumeItem{Additionally optimized and developed stored-procedures in \textbf{MS SQL Server}.}
            \resumeItem{Applied reporting solutions for operational staff to support process requirements, which increased \newline operational efficiency by \textbf{30\%}.}
            \resumeItem{Build IMAP protocol based email reader to fetch the emails from the mailbox 
            \newline on a real-time basis  using \textbf{Flask} and \textbf{MySQL}}
      \resumeItemListEnd
      

    \resumeSubheading
      {Software Engineer Intern}{May 2021 -- Aug. 2021}
      {NUZPAPR TECHNOLOGIES}{Delhi, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented web-app using \textbf{Nextjs, Nodejs} and
\textbf{MongoDB} and a chat application \newline with \textbf{AES-256bit} encryption and
push notifications using \textbf{websockets}.}
        \resumeItem{Improved test coverage by setting up an end-to-end test
framework \textbf{cypressIO} to reduce the \newline risk of breaking production
after the addition of new engineers on the project.}
        \resumeItem{Deployed the app on \textbf{AWS EC2} server and implemented CI/CD
using \textbf{TravisCI}.}
    
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{Mar. 2021 -- Apr. 2021}
      {COGNIABLE}{Delhi, India}
      \resumeItemListStart
        \resumeItem{Build backend APIs in \textbf{Django} and \textbf{GraphQL} and frontend in
ReactJS and Redux.}
        \resumeItem{Reduced error by \textbf{24\%} by implementing TDD with \textbf{PyTest}.}
        \resumeItem{Spearheaded and constructed \textbf{docker} containers for reactjs and nodejs applications.}

      \resumeItemListEnd
      
      
    \resumeSubheading
      {Software Engineer Intern}{Jun. 2019 -- Jul. 2019}
      {XLNC TECHNOLOGY}{Delhi, India}
      \resumeItemListStart
        \resumeItem{Independently designed and developed Python automation scripts using \textbf{Selenium} \newline to simplify data gathering, saving the organization \textbf{150+} dev hours per month.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Dysfunctionally Functional} $|$ {\href{https://github.com/Chinmay-395/Principles-Of-Programming}{\faIcon{github}} } }{Sep. 2022 -- Present}
          \resumeItemListStart
            \resumeItem{Implemented a interpreter for my own language built using OCaml a functional programming language}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Smart Spoon} $|$ {\href{https://github.com/Chinmay-395/Smart-Spoon}{\faIcon{github}} } }{Aug. 2018 -- Dec. 2018}
          \resumeItemListStart
            \resumeItem{An IOT device for parkinson's patient for counteracting the tremor using IMU(Accelerometer) \newline sensor and Arduino, written in C++.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd



%
%-----------Achievements-----------
\section{Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
        \item{
            \textbf{Hackerrank}{: 5 stars in C++} \\
            \textbf{Stackoverflow}{: 340 reputation, 5 silver badges and 14 bronze badges.} \\
            \textbf{Leetcode}{: Solved 300+ problems and have 2 badges.} \\
        }
    }
 \end{itemize}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
        \item{
            \textbf{Languages}{: JavaScript/Typescript, Python, C/C++, C\#, SQL, Java, OCaml} \\
            \textbf{Frameworks}{: React,Redux, GraphQL, Node.js, Flask, Django, ASP.NET, CypressIO, Py-Test, Travis-CI} \\
            \textbf{Database}{: MS SQL Server, MySQL, PostgreSQL, Redis, MongoDB} \\
            
        }
    }
 \end{itemize}


%-------------------------------------------
\end{document}
